Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-19 tex/sections/intro.tex
Fix readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block gets certified by all members of the delegates committee and after that it required to get approved
by its corresponding validator committee.

Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the Argennon network.
Every committee of validators has an index between $0$ and $m - 1$, and is responsible for validating block number $n$,
if $n$ modulo $m$ equals the committee index. A block is approved if it takes approval votes from at least $2/3$ of
the total stake of its validator committee.

@@

In Argennon, a block is considered final after its \textbf{next} block gets certified by \textbf{both} delegates and
validator committees.
The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

Centralized block generation brings some interesting features to the Argennon platform, such as flexible and lower
fees, off chain fee payment, optimistic instant transaction confirmation, and runoff protection.
However, it also increases the possibility of transaction censorship. In Argennon, this problem is addressed by a
special High Priority Request (HPR) protocol.

@@

More formally, each CI statement has the form $\tau(\mathbb{S}, \mathbb{R}, \hat{\mathbb{S}})$, and states that
$\hat{\mathbb{S}}$ is the commitment of the next state after executing an ordered list of external requests with commitment
$\mathbb{R}$ on a state with commitment $\mathbb{S}$.
Commitments to states are produced by a cryptographic accumulator.
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud and efficiently validate a block.

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent of each other and can be done in parallel. As a result, a validator can use
multiple cores for verifying CI statements of a \textbf{single} block and different validator committees can
simultaneously and
independently verify \textbf{different} blocks.
In addition, proof generation of different CI statements similarly can be done in parallel. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing external requests and
generating the state transition as fast as possible.

@@

Using succinct argument of knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. To reduce the execution fee, this validator
contract could be used for validating roll-ups of state transition.

>>>>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block gets certified by all members of the delegates committee and after that it must get approved
by its corresponding validator assembly.

Validator assemblies are very
large sets of validators including at least three percent of the maximum possible stake of the Argennon network.
Every validator assembly has an index between $0$ and $m - 1$, and is responsible for validating block number $n$,
if $n$ modulo $m$ equals the index of the assembly. A block is approved if it takes approval votes from at
least $2/3$ of the total stake of its validator assembly.

@@

In Argennon, a block is considered final after its \textbf{next} block gets certified by \textbf{both} the
delegates committee and its validator assembly.
The Argennon protocol ensures that as long as more than half of the total stake of validators is
controlled by honest users, the probability of discarding a final block is near zero even if all the delegates are
malicious.

Centralized block generation brings some interesting features to the Argennon platform, such as flexible and lower
fees, off chain fee payment, optimistic instant transaction confirmation, and front running protection.
However, it also increases the possibility of transaction censorship. In Argennon, this problem is addressed by a
special High Priority Request (HPR) protocol.

@@

More formally, each CI statement has the form $\tau_{\mathbb{S}, \hat{\mathbb{S}}, \mathbb{R}}$, and states that
$\hat{\mathbb{S}}$ is the commitment of the next state after executing an ordered list of external requests with
commitment $\mathbb{R}$ on a state which has commitment $\mathbb{S}$.
Commitments to states are produced by a cryptographic accumulator.
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud and validate blocks without storing the ledger state
or performing costly computation.

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent of each other and can be done in parallel. As a result, a validator can use
multiple cores for verifying CI statements of a \textbf{single} block and different validator assemblies can
simultaneously and
independently verify \textbf{different} blocks.
In addition, proof generation of different CI statements similarly can be done in parallel. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing external requests and
generating the state transition as fast as possible.

@@

Using succinct argument of knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets to the Argennon blockchain. To reduce the execution fee, this validator
contract could be used for validating only roll-ups of state transition.
